---
title: "Getting Started with "
author: "Nishant Mishra"
date: "02/05/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
library(binomial)
```

## Binomial Package

The package `"binomial"` is an encompassing binomial package for simulating binomial probability given a certain number of trials and given a certain probability.

## Checker Functions

The package encompasses various checker functions to determine if variables are valid inputs, as exemplified below

```{r}
check_prob(0.5)
check_trials(5)
check_success(3, 5)
```

## Private Auxiliary Functions
There are various auxiliar functions that take two arguments: `"trials"` and `"prob"`, as exemplified below:
```{r}
aux_mean(10, 0.3)
aux_variance(10, 0.3)
aux_mode(10, 0.3)
aux_skewness(10, 0.3)
aux_kurtosis(10, 0.3)
```

## Binomial Probabilities
The `"bin_choose"` function calculates the number of combinations in which k successes can occur in trials, as seen below:
```{r}
bin_choose(n = 5, k = 2)
```

The `"bin_probability"` function calculates the binomial probability, and can be used for vectorized numbers of successes too
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)
```

The `"bin_distribution"` function calculates a data frame of a binomial distribution, as can be seen below:
```{r}
bin_distribution(trials = 5, prob = 0.5)
```

The `"bin_cumulative"` function calculates a cumulative data frame of a binomial distribution, as can be seen below:
```{r}
bin_cumulative(trials = 5, prob = 0.5)
```

The `"bin_variable"` function calculates a 
